Through the eyes of the teacher

### 2022-03-01 02_paper/01_pilot/paper_1_supplement_questionnaire.Rmd
r markdown method part

---
title             : "Through the eyes of the teacher"
shorttitle        : "Visual attention in teaching and learning processes"

@@

### Behavioral data

The speech, sounds and voices were recorded with an audio recorder installed in the middle of the Lab. Movements, facial expressions and gestures of the subjects were recorded by four cameras from different angles. One camera was installed to film the class from the side. Two more cameras were installed on the blackboard and at the end of the Lab to film the teacher and class from the front and back. Furthermore, the fourth camera was installed in such a way that only facial expressions and gestures of the teacher were recorded, which enables a semi-automated analysis of the movement sequences.

### Eyetracking data

A binocular Tobii Pro Glasses 2 eye-tracker consisting of a wearable head unit and a recording unit was used to record the eye movements of all 8 participants. The head unit is a measuring device with different sensitive sensors. A high-definition scene camera captures a full HD video and an integrated microphone records the surrounding sounds. Infrared light illuminators support the eye tracking sensors which record the eye orientation. The videos were recorded with a sampling rate of 50 Hz and a video resolution with 1920 x 1080 at 25 frames per second. The scene camera has a field of view of 90 deg. in 16:9 format (82 deg. horizontal and 52 deg. vertical) and has a frame dimension of 179 x 159 x 57mm (width x depth x height). The Tobii Pro Glasses Controller software was used to record and calibrate the eye movements.

@@

# # item analysis of a scale or index using the tab_itemscale() function of the sjPlot package
# 
# # activation & support
# tab_itemscale(stud.as.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# 
# # classroom management
# tab_itemscale(stud.cm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# 
# # clarity & structuredness
# tab_itemscale(stud.cs.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# 
# # natural behaviour
# tab_itemscale(stud.nb.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# 
# # positive clima and motivation
# tab_itemscale(stud.pcm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# 
# # presence without subscales
# tab_itemscale(stud.p.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# 
# # presence: posture & gaze
# tab_itemscale(stud.ppg.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# # presence: voice
# tab_itemscale(stud.pv.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# # presence: verbal/non-verbal intervention
# tab_itemscale(stud.pvni.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)

@@

\newpage
The individual items of a scale are further represented in graphs.

@@

# to create error bars, we need to summarize the data in a separate data frame
cm.plot.sd <- cm.data %>%
  group_by(group, item.wordings, .drop=TRUE) %>%
  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# long plot
cm.plot<-ggplot(data = cm.plot.sd,
                  aes(x = item.wordings, y = mean,
                      group = perspective, colour = perspective)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,4)+
  facet_grid(~perspective)+
  labs(data = cm.data, y = "value", x = NULL,
       title="Classroom management" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 6))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
cm.plot

@@

# to create error bars, we need to summarize the data in a separate data frame
pcm.plot.sd <- pcm.data %>%
  group_by(group, item.wordings, .drop=TRUE) %>%
  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# long plot
pcm.plot<-ggplot(data = pcm.plot.sd,
                  aes(x = item.wordings, y = mean,
                      group = group, colour = group)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,4)+
  facet_grid(~perspective)+
  labs(data = pcm.data, y = "value", x = NULL,
       title="Positive climate and motivation" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 5))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
pcm.plot

@@

# to create error bars, we need to summarize the data in a separate data frame
cs.plot.sd <- cs.data %>%
  group_by(group, item.wordings, .drop=TRUE) %>%
  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# long plot
cs.plot<-ggplot(data = cs.plot.sd,
                  aes(x = item.wordings, y = mean,
                      group = group, colour = group)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,4)+
  facet_grid(~perspective)+
  labs(data = cs.data, y = "value", x = NULL,
       title="Clarity and structuredness" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 6))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
cs.plot

```
\newpage
(4) Activation and support
```{r Activation and support line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Activation and support"}

### Activation and support

@@

# to create error bars, we need to summarize the data in a separate data frame
as.plot.sd <- as.data %>%
  group_by(group, item.wordings, .drop=TRUE) %>%
  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# long plot
as.plot<-ggplot(data = as.plot.sd,
                  aes(x = item.wordings, y = mean,
                      group = group, colour = group)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,4)+
  facet_grid(~perspective)+
  labs(data = as.data, y = "value", x = NULL,
       title="Activation and support" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 6))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
as.plot

@@

(ref:presenceposturegaze-caption) (5) Presence: posture/gaze

```{r presenceposturegaze, fig.cap = "(ref:presenceposturegaze-caption)", fig.align = "center", echo = FALSE}

knitr::include_graphics("./pictures/presenceposturegaze.png", dpi = 108)

# ```{r Presence: posture/gaze line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}

# ### Presence: posture/gaze 
# 
# # filter by parameter variable, i.e. create a subset for Presence: posture/gaze
# ppg.data <- quest.raw.data %>% filter(scale == "Presence: posture/gaze")
# 
# # value sometimes contained text before filtering, we have to convert the numbers to numeric
# ppg.data <- ppg.data %>%  mutate(value = as.numeric(as.character(factor(value))))
# 
# # to create error bars, we need to summarize the data in a separate data frame
# ppg.plot.sd <- ppg.data %>%
#   group_by(group, item.wordings, .drop=TRUE) %>%
#   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
# 
# # long plot
# ppg.plot<-ggplot(data = ppg.plot.sd,
#                   aes(x = item.wordings, y = mean,
#                       group = group, colour = group)) +
#   geom_line()+
#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
#   theme_light() +
#   ylim(1,4)+
#   facet_grid(~perspective)+
#   labs(data = ppg.data, y = "value", x = NULL,
#        title="Presence: posture/gaze" ,
#        subtitle=NULL)+
#   theme(legend.position="bottom",
#         panel.spacing.x = ,
#         plot.title = element_text(hjust = 0.5),
#         axis.text.y = element_text(size = 6))+
#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
#   coord_flip()
# ppg.plot

@@

(ref:presencevoice-caption) (6) Presence: voice

```{r presencevoice, fig.cap = "(ref:presencevoice-caption)", fig.align = "center", echo = FALSE}

knitr::include_graphics("./pictures/presencevoice.png", dpi = 108)

# ```{r Presence: voice line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
# 
# ### Presence: voice 
# # filter by parameter variable, i.e. create a subset for Presence: voice
# pv.data <- quest.raw.data %>% filter(scale == "Presence: voice")
# 
# # value sometimes contained text before filtering, we have to convert the numbers to numeric
# pv.data <- pv.data %>%  mutate(value = as.numeric(as.character(factor(value))))
# 
# # to create error bars, we need to summarize the data in a separate data frame
# pv.plot.sd <- pv.data %>%
#   group_by(group, item.wordings, .drop=TRUE) %>%
#   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
# 
# # long plot
# pv.plot<-ggplot(data = pv.plot.sd,
#                   aes(x = item.wordings, y = mean,
#                       group = group, colour = group)) +
#   geom_line()+
#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
#   theme_light() +
#   ylim(1,4)+
#   facet_grid(~perspective)+
#   labs(data = pv.data, y = "value", x = NULL,
#        title="Presence: voice" ,
#        subtitle=NULL)+
#   theme(legend.position="bottom",
#         panel.spacing.x = ,
#         plot.title = element_text(hjust = 0.5),
#         axis.text.y = element_text(size = 6))+
#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
#   coord_flip()
# pv.plot

@@

(ref:presenceverbalnonverbalintervention-caption) (7) Presence: verbal and non-verbal intervention

```{r presenceverbalnonverbalintervention, fig.cap = "(ref:presenceverbalnonverbalintervention-caption)", fig.align = "center", echo = FALSE}

knitr::include_graphics("./pictures/presenceverbalnonverbalintervention.png", dpi = 108)

# ```{r Presence: verbal and non-verbal intervention line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
# 
# ### Presence: verbal and non-verbal intervention 
# # filter by parameter variable, i.e. create a subset for Presence: verbal and non-verbal intervention
# pvni.data <- quest.raw.data %>% filter(scale == "Presence: verbal and non-verbal intervention")
# 
# # value sometimes contained text before filtering, we have to convert the numbers to numeric
# pvni.data <- pvni.data %>%  mutate(value = as.numeric(as.character(factor(value))))
# 
# # to create error bars, we need to summarize the data in a separate data frame
# pvni.plot.sd <- pvni.data %>%
#   group_by(group, item.wordings, .drop=TRUE) %>%
#   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
# 
# # long plot
# pvni.plot<-ggplot(data = pvni.plot.sd,
#                   aes(x = item.wordings, y = mean,
#                       group = group, colour = group)) +
#   geom_line()+
#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
#   theme_light() +
#   ylim(1,4)+
#   facet_grid(~perspective)+
#   labs(data = pvni.data, y = "value", x = NULL,
#        title="Presence: verbal and non-verbal intervention" ,
#        subtitle=NULL)+
#   theme(legend.position="bottom",
#         panel.spacing.x = ,
#         plot.title = element_text(hjust = 0.5),
#         axis.text.y = element_text(size = 6))+
#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
#   coord_flip()
# pvni.plot

@@

# to create error bars, we need to summarize the data in a separate data frame
nb.plot.sd <- nb.data %>%
  group_by(group, item.wordings, .drop=TRUE) %>%
  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# long plot
nb.plot<-ggplot(data = nb.plot.sd,
                  aes(x = item.wordings, y = mean,
                      group = group, colour = group)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,4)+
  facet_grid(~perspective)+
  labs(data = nb.data, y = "value", x = NULL,
       title="Natural behaviour" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 6))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
nb.plot

```
\newpage
In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.

```{r boxplot scales, fig.width=6, fig.height = 8, echo = FALSE, fig.cap = "Boxplots and individual data for experts and novices"}

quest.plot <- quest.raw.data %>%
  ggplot(aes(x=scale, y=value, fill=scale)) +
    geom_boxplot() +
    scale_x_discrete(guide = guide_axis(angle = 70)) +
    geom_jitter(color="black", size=0.4, alpha=0.5) +
    theme_light() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)) +
    facet_grid(~group)+
    ggtitle("Boxplot with individual points for all scales") +
    xlab("")
quest.plot

@@

### Behavioral Data

The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters [@kuckartz2019analyzing]. The following coding scheme was developed:

- phase - lesson begin, state event: teacher starts the lesson with a noise, talk, taking a position in class
- phase - lesson end,	state event: teacher finishes the lesson with a noise, talk, taking a position in class
- phase - organization/transition points, state event: any situation that does not imply effective learning time (fetching chalk, working        material, organizing desks, opening windows, printing work results etc.)
- phase - single,	state event: any individual student activity on a given task (reading, writing, drawing etc.)
- phase - group, state event: any student activity on a given task together in a group of at least 3 students (reading, writing, drawing etc.)
- phase - class discussion, state event: discussion in class, teacher talks to class/individual/group
- phase - pair: state event: any student activity on a given task together in a team of 2 students (reading, writing, drawing etc.)
- phase - teachers lecture, state event: any teacher's presentation on a certain topic which maybe supported by a PPP, PREZI, notes on board,    OHP etc.
- phase - other, state event: not categorizable
- phase - break, state event: e.g. drinking, relaxation exercises
- phase - external interruption, state event: external interruptions (e.g. fire alarm, technical problems, other teachers coming into the room)

- speaking time - teacher, state event
- speaking time - students, state event

- disruption - chatting with neighbor, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
- disruption - asking a question, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
- disruption - yelling, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
- disruption - looking at phone, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
- disruption - staring out of window, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
- disruption - drawing, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
- disruption - head on table, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
- disruption - clicking pen, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
- disruption - drumming hands, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
- disruption - walking around, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)

First, we coded the speaking time of the teacher and the students to compare all perspectives: coder, observer, students, teacher. The graph below shows the result of the coded speaking duration compared to the estimated speaking duration assessed with the questionnaire.

```{r coded speaking time, echo = FALSE }
### read in data for 01_01_expert_D
speaking.data.01.01 <- read.delim("./data/Aperol_pilot_01_01_expert_D_cam4_AL_MK.txt", dec=",", sep="\t", header=T)

### select relevant columns
speaking.data.01.01 <- speaking.data.01.01  %>% select(
  Dokumentgruppe,
  Dokumentname,
  Code,
  Anfang,
  Ende,
  Fläche,
  Abdeckungsgrad..)

### filter only speaking time of teacher and "kodiert von Anna" as row 
speaking.data.01.01 <- speaking.data.01.01 %>% filter (Code == "speaking time\\teacher",
                                           Dokumentgruppe == "kodiert von Anna")
speaking.data.01.01 <- sum(speaking.data.01.01$Abdeckungsgrad..)

# read in data for 01_02_expert_A
speaking.data.01.02 <- read.delim("./data/Aperol_pilot_01_02_expert_A_cam1_AL.txt", dec=",", sep="\t", header=T)

### select relevant columns
speaking.data.01.02 <- speaking.data.01.02 %>% select(
  Dokumentname,
  Code,
  Anfang,
  Ende,
  Fläche,
  Abdeckungsgrad..)

### filter only speaking time of teacher as row 
speaking.data.01.02 <- speaking.data.01.02 %>% filter (Code == "speaking time\\teacher")
speaking.data.01.02 <- sum(speaking.data.01.02$Abdeckungsgrad..)

# read in data for 01_03_novice_B
speaking.data.01.03 <- read.delim("./data/Aperol_pilot_01_03_novice_B_cam1.txt", dec=",", sep="\t", header=T)

### select relevant columns
speaking.data.01.03 <- speaking.data.01.03 %>% select(
  Code,
  Anfang,
  Ende,
  Fläche,
  Abdeckungsgrad..)

### filter only speaking time of teacher as row 
speaking.data.01.03 <- speaking.data.01.03 %>% filter (Code == "speaking time\\teachter")
speaking.data.01.03 <- sum(speaking.data.01.03$Abdeckungsgrad..)

# read in data for 01_04_novice_C
speaking.data.01.04 <- read.delim("./data/Aperol_pilot_01_04_novice_C_cam1.txt", dec=",", sep="\t", header=T)

### select relevant columns
speaking.data.01.04 <- speaking.data.01.04 %>% select(
  Code,
  Anfang,
  Ende,
  Fläche,
  Abdeckungsgrad..)

### filter only speaking time of teacher as row 
speaking.data.01.04 <- speaking.data.01.04 %>% filter (Code == "speaking time\\teachter")

speaking.data.01.04 <- sum(speaking.data.01.04$Abdeckungsgrad..)

# read in data for 02_01_novice_A
speaking.data.02.01 <- read.delim("./data/Aperol_pilot_02_01_novice_A_glasses.txt", dec=",", sep="\t", header=T)

### select relevant columns
speaking.data.02.01 <- speaking.data.02.01 %>% select(
  Code,
  Anfang,
  Ende,
  Fläche,
  Abdeckungsgrad..)

### filter only speaking time of teacher as row 
speaking.data.02.01 <- speaking.data.02.01 %>% filter (Code == "speaking time\\teacher")
speaking.data.02.01 <- sum(speaking.data.02.01$Abdeckungsgrad..)

# read in data for 02_02_novice_B
speaking.data.02.02 <- read.delim("./data/Aperol_pilot_02_02_novice_B_cam1_AL_MK.txt", dec=",", sep="\t", header=T)

### select relevant columns
speaking.data.02.02 <- speaking.data.02.02 %>% select(
  Dokumentgruppe,
  Code,
  Anfang,
  Ende,
  Fläche,
  Abdeckungsgrad..)

### filter only speaking time of teacher as row 
speaking.data.02.02 <- speaking.data.02.02 %>% filter (Code == "speaking time\\teacher",
                                                       Dokumentgruppe == "kodiert von Anna")
speaking.data.02.02 <- sum(speaking.data.02.02$Abdeckungsgrad..)

# read in data for 02_03_novice_C
speaking.data.02.03 <- read.delim("./data/Aperol_pilot_02_03_novice_C_cam1_AL_MK.txt", dec=",", sep="\t", header=T)

### select relevant columns
speaking.data.02.03 <- speaking.data.02.03 %>% select(
  Dokumentgruppe,
  Code,
  Anfang,
  Ende,
  Fläche,
  Abdeckungsgrad..)

### filter only speaking time of teacher as row 
speaking.data.02.03 <- speaking.data.02.03 %>% filter (Code == "speaking time\\teachter",
                                                       Dokumentgruppe == "02_03_kodiert von Anna")
speaking.data.02.03 <- sum(speaking.data.02.03$Abdeckungsgrad..)

# read in data for 02_04_novice_D
speaking.data.02.04 <- read.delim("./data/Aperol_pilot_02_04_novice_D_cam1.txt", dec=",", sep="\t", header=T)

### select relevant columns
speaking.data.02.04 <- speaking.data.02.04 %>% select(
  Code,
  Anfang,
  Ende,
  Fläche,
  Abdeckungsgrad..)

### filter only speaking time of teacher as row 
speaking.data.02.04 <- speaking.data.02.04 %>% filter (Code == "speaking time\\teachter")
speaking.data.02.04 <- sum(speaking.data.02.04$Abdeckungsgrad..)

```{r speaking plot, echo=FALSE}

# read in table with coded speaking time included
speaking.data <- read.delim("./data/plus_coded_speaking_time_questionnaire_data_0802.txt", dec=",", sep="\t", header=T)

# to compare both sessions filter only Identical items
speaking.data <- speaking.data  %>% filter(str_detect(scale, 
                                                 paste(c("Duration of speaking time"),
                                                    collapse = '|')))

# value sometimes contained text before filtering, we have to convert the numbers to numeric
speaking.data <- speaking.data %>%  mutate(value = as.numeric(value))

speaking.plot <- speaking.data %>%
  ggplot(aes(x='Duration of speaking time', y=value, fill=group)) +
    geom_boxplot() +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    theme_light() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11),
      axis.text.x = element_text(size = 8)) +
    facet_grid(group~perspective) +
    ggtitle("Boxplot with individual points for Duration of speaking time") +
    xlab("")
speaking.plot

### Eyetracking Data

>>>>

---
title             : "Through the eyes of the teacher"
shorttitle        : "Visual attention in teaching and learning processes - QUESTIONNAIRE DATA"

@@

@@

# item analysis of a scale or index using the tab_itemscale() function of the sjPlot package

# # activation & support
# tab_itemscale(stud.as.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# 
# # classroom management
# tab_itemscale(stud.cm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# 
# # clarity & structuredness
# tab_itemscale(stud.cs.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# 
# # natural behaviour
# tab_itemscale(stud.nb.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# 
# # positive clima and motivation
# tab_itemscale(stud.pcm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# 
# # presence without subscales
# tab_itemscale(stud.p.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# 
# # presence: posture & gaze
# tab_itemscale(stud.ppg.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# # presence: voice
# tab_itemscale(stud.pv.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# # presence: verbal/non-verbal intervention
# tab_itemscale(stud.pvni.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)

@@

```
\newpage
The individual items of a scale are further represented in graphs.

@@

# to create error bars, we need to summarize the data in a separate data frame
cm.plot.sd <- cm.data %>%
  group_by(group, shortID, .drop=TRUE) %>%
  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# long plot
cm.plot<-ggplot(data = cm.plot.sd,
                  aes(x = shortID, y = mean,
                      group = perspective, colour = perspective)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,4)+
  facet_grid(~perspective)+
  labs(data = cm.data, y = "value", x = NULL,
       title="Classroom management" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 6))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
cm.plot

@@

# to create error bars, we need to summarize the data in a separate data frame
pcm.plot.sd <- pcm.data %>%
  group_by(group, shortID, .drop=TRUE) %>%
  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# long plot
pcm.plot<-ggplot(data = pcm.plot.sd,
                  aes(x = shortID, y = mean,
                      group = group, colour = group)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,4)+
  facet_grid(~perspective)+
  labs(data = pcm.data, y = "value", x = NULL,
       title="Positive climate and motivation" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 5))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
pcm.plot

@@

# to create error bars, we need to summarize the data in a separate data frame
cs.plot.sd <- cs.data %>%
  group_by(group, shortID, .drop=TRUE) %>%
  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# long plot
cs.plot<-ggplot(data = cs.plot.sd,
                  aes(x = shortID, y = mean,
                      group = group, colour = group)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,4)+
  facet_grid(~perspective)+
  labs(data = cs.data, y = "value", x = NULL,
       title="Clarity and structuredness" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 6))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
cs.plot

```
\newpage
(4) Activation and support
```{r Activation and support line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Activation and support"}
### Activation and support

@@

# to create error bars, we need to summarize the data in a separate data frame
as.plot.sd <- as.data %>%
  group_by(group, shortID, .drop=TRUE) %>%
  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# long plot
as.plot<-ggplot(data = as.plot.sd,
                  aes(x = shortID, y = mean,
                      group = group, colour = group)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,4)+
  facet_grid(~perspective)+
  labs(data = as.data, y = "value", x = NULL,
       title="Activation and support" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 6))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
as.plot

@@

(5) Presence: posture and gaze 
```{r Presence posture and gaze line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Presence posture and gaze"}

# ### Presence: posture/gaze
#
# filter by parameter variable, i.e. create a subset for Presence: posture/gaze
ppg.data <- quest.raw.data %>% filter(scale == "Presence: posture/gaze")
#
# value sometimes contained text before filtering, we have to convert the numbers to numeric
ppg.data <- ppg.data %>%  mutate(value = as.numeric(as.character(factor(value))))

# to create error bars, we need to summarize the data in a separate data frame
ppg.plot.sd <- ppg.data %>%
  group_by(group, shortID, .drop=TRUE) %>%
  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# long plot
ppg.plot<-ggplot(data = ppg.plot.sd,
                        aes(x = shortID, y = mean,
                        group = group, colour = group)) +
    geom_line()+
    geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
    theme_light() +
     ylim(1,4)+
     facet_grid(~perspective)+
     labs(data = ppg.data, y = "value", x = NULL,
         title="Presence: posture/gaze" ,
         subtitle=NULL)+
    theme(legend.position="bottom",
          panel.spacing.x = ,
          plot.title = element_text(hjust = 0.5),
          axis.text.y = element_text(size = 6))+
    scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
   coord_flip()
 ppg.plot

@@

(6) Presence: voice
```{r Presence voice line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Presence voice"}

### Presence: voice
# filter by parameter variable, i.e. create a subset for Presence: voice
pv.data <- quest.raw.data %>% filter(scale == "Presence: voice")

# value sometimes contained text before filtering, we have to convert the numbers to numeric
pv.data <- pv.data %>%  mutate(value = as.numeric(as.character(factor(value))))

# to create error bars, we need to summarize the data in a separate data frame
pv.plot.sd <- pv.data %>%
  group_by(group, shortID, .drop=TRUE) %>%
  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# long plot
pv.plot<-ggplot(data = pv.plot.sd,
                  aes(x = shortID, y = mean,
                      group = group, colour = group)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,4)+
  facet_grid(~perspective)+
  labs(data = pv.data, y = "value", x = NULL,
       title="Presence: voice" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 6))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
pv.plot

@@

(7) Presence: verbal and non-verbal intervention

```{r Presence verbal and non-verbal intervention line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}

### Presence: verbal and non-verbal intervention
# filter by parameter variable, i.e. create a subset for Presence: verbal and non-verbal intervention
pvni.data <- quest.raw.data %>% filter(scale == "Presence: verbal and non-verbal intervention")

# value sometimes contained text before filtering, we have to convert the numbers to numeric
pvni.data <- pvni.data %>%  mutate(value = as.numeric(as.character(factor(value))))

# to create error bars, we need to summarize the data in a separate data frame
pvni.plot.sd <- pvni.data %>%
  group_by(group, shortID, .drop=TRUE) %>%
  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# long plot
pvni.plot<-ggplot(data = pvni.plot.sd,
                  aes(x = shortID, y = mean,
                      group = group, colour = group)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,4)+
  facet_grid(~perspective)+
  labs(data = pvni.data, y = "value", x = NULL,
       title="Presence: verbal and non-verbal intervention" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 6))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
pvni.plot

@@

# to create error bars, we need to summarize the data in a separate data frame
nb.plot.sd <- nb.data %>%
  group_by(group, shortID, .drop=TRUE) %>%
  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# long plot
nb.plot<-ggplot(data = nb.plot.sd,
                  aes(x = shortID, y = mean,
                      group = group, colour = group)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,4)+
  facet_grid(~perspective)+
  labs(data = nb.data, y = "value", x = NULL,
       title="Natural behaviour" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 6))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
nb.plot

```
\newpage
In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.
```{r boxplot scales, fig.width=6, fig.height = 8, echo = FALSE, fig.cap = "Boxplots and individual data for experts and novices"}

quest.plot <- quest.raw.data %>%
  ggplot(aes(x=scale, y=value, fill=scale)) +
    geom_boxplot() +
    scale_x_discrete(guide = guide_axis(angle = 70)) +
    geom_jitter(color="black", size=0.4, alpha=0.5) +
    theme_light() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)) +
    facet_grid(~perspective)+
    ggtitle("Boxplot with individual points for all scales") +
    xlab("")
quest.plot

@@
